### 2017-01-30 manuscript.rmd
Update manuscript.rmd
Minor fix to citation of PIC

We reanalyzed the the KMRR study using phylogenetic comparative methods, focusing on the dataset of Brawand *et al.* 2011 [@Brawand:2011du]. For each internal node in each gene tree (Figure 1b), we measured the phylogenetic independent contrast [@Felsenstein:1985ua] (PIC) of the expression statistic Tau. This is the difference in values of Tau for descendant nodes scaled by the expected variance (determined largely by the lengths of these branches). These contrasts were then annotated by whether they are made across a speciation or duplication event. The original description of independent contrasts [@Felsenstein:1985ua] focused on assessing covariance between changes in two traits on a tree. Our use of contrasts is a bit different-- we look for differences in evolutionary changes of one trait (differential expression) between two categories of nodes (speciation and duplication) on a tree.

>>>>

We reanalyzed the the KMRR study using phylogenetic comparative methods, focusing on the dataset of Brawand *et al.* 2011 [@Brawand:2011du]. For each internal node in each gene tree (Figure 1b), we measured the phylogenetic independent contrast (PIC) [@Felsenstein:1985ua] of the expression statistic Tau. This is the difference in values of Tau for descendant nodes scaled by the expected variance (determined largely by the lengths of these branches). These contrasts were then annotated by whether they are made across a speciation or duplication event. The original description of independent contrasts [@Felsenstein:1985ua] focused on assessing covariance between changes in two traits on a tree. Our use of contrasts is a bit different-- we look for differences in evolutionary changes of one trait (differential expression) between two categories of nodes (speciation and duplication) on a tree.
